Contracts for unions and intersections are hard for Nickel

### 2021-05-25 paper.tex
small fixes sec 5

Another difficult issue Keil and Thiemann were able to solve, is the
fact that flat contracts and intersection do not usually play nice
together.
\todo{This assumes the difficulty was already explained}
They provide two different sets of rules for their calculus,
the first one is non deterministic, whose purpose is to provide
semantics that are simple to understand.
The second one is a deterministic set of rules, that are intended
to be simple to implement.
This second set needs to perform operations
on the evaluation context, to decide whether or not to evaluate
a given contract.

We see two problems here, a minor one is the fact that two different
semantics need to be defined, which translates either to a difficult
to implement or a difficult to understand system
\unsure{(Yann) Is it really a
    problem per se? It is common thing to do (a nice declarative system
    for proofs and an algorithmic one for implementation, proved equivalent).
    Maybe the point is that the algorithmic system is way more complex than the
declarative one
(Teo) I think you're right, I'll try to reword it}.
A second, major one,
is the dependency added over the evaluation context, since, again,
it makes composing this, with other features desired on programming languages,
difficult, or even impossible (as the case with common subexpression
elimination)\unsure{(Yann) I think we need to substantiate this claim. If this
context dependency explains why CSE is invalid, maybe have a little example?}
\todo{(Yann) TODO: see if there's a low hanging complexity
    argument we can make (like it's quadratic in the number of open contracts or
whatever)}.

>>>>

Another difficult issue Keil and Thiemann were able to solve, is the
fact that flat contracts and intersection do not usually play nice
together.
They provide two different sets of rules for their calculus,
the first one is non deterministic, whose purpose is to provide
semantics that are simple to understand.
The second one is a deterministic set of rules, that are intended
to be simple to implement.
This second set needs to perform operations
on the evaluation context, to decide whether or not to evaluate
a given contract.
\unsure{Worth showing how the non deterministic version works? (See section B.1.1)}

We see two problems here, a minor one is the fact that the two
different semantics defined for the calculus are really far apart
one from the other, both on the strategies used for contract resolution,
as well as on the complexity levels.
\unsure{(Yann) Is it really a
    problem per se? It is common thing to do (a nice declarative system
    for proofs and an algorithmic one for implementation, proved equivalent).
    Maybe the point is that the algorithmic system is way more complex than the
declarative one
(Teo) reworded}.
A second, major one,
is the dependency added over the evaluation context, since, again,
it makes composing this, with other features desired on programming languages,
difficult, or even impossible
\unsure{(Yann) I think we need to substantiate this claim. If this
context dependency explains why CSE is invalid, maybe have a little example?
(Teo) I removed it, I don't think there's an example, mainly since
this context dependency is not part of the language. I do think it complicates
implementation of said feature}
\todo{(Yann) TODO: see if there's a low hanging complexity
    argument we can make (like it's quadratic in the number of open contracts or
whatever)}.
